High-order cognition is supported by complex but compressible brain activity patterns

### 2023-02-20 paper/main.tex
checking  in some thoughts, minor file reorganization

\title{Understanding brain complexity in naturalistic processing
in humans} \author{Lucy
  L. W. Owen$^1$, and\
  Jeremy R. Manning\textsuperscript{$1, \dagger$}\\
  [0.1in]$^1$Department of Psychological and Brain
  Sciences,\\Dartmouth
  College, Hanover, NH\\
  \textsuperscript{$\dagger$}Address correspondence to
  jeremy.r.manning@dartmouth.edu}

@@

\begin{abstract}
We applied dimensionality reduction algorithms to the activity patterns in each experimental condition.  Specifically, we sought to understand the “dimensionality” of the neural patterns that were sufficient to decode participants’ listening times (or approach was similar to that of Mack et al. 2017).  We found that even low-dimensional embeddings of the data were sufficient to accurately decode listening times from the intact story recording, whereas finer temporal scramblings of the story required higher-dimensional embeddings of the data to reach peak decoding accuracy.
\end{abstract}

@@

>>>>

\title{High-order cognition is supported by complex but compressible brain activity patterns}

\author{Lucy L. W. Owen$^1, 2$, and Jeremy R. Manning\textsuperscript{$1,
*$}\\$^1$Department of Psychological and Brain Sciences,\\Dartmouth College,
Hanover, NH\\[0.1cm]$^2$Carney Institute for Brain Sciences,\\Brown University,
Providence, RI\\[0.1cm] \textsuperscript{*}Address correspondence to
jeremy.r.manning@dartmouth.edu}

@@

\begin{abstract}

We applied dimensionality reduction algorithms to the activity
patterns in each experimental condition. Specifically, we sought to understand
the “dimensionality” of the neural patterns that were sufficient to decode
participants’ listening times (or approach was similar to that of Mack et al.
2017). We found that even low-dimensional embeddings of the data were
sufficient to accurately decode listening times from the intact story
recording, whereas finer temporal scramblings of the story required
higher-dimensional embeddings of the data to reach peak decoding accuracy.

\end{abstract}

@@

Large-scale networks, including the human brain, may be conceptualized as
occupying one or more positions along on a continuum. At one extreme, every
node is fully independent of every other node. At the other extreme, all nodes
are fully coupled and behave identically. Each extreme optimizes key properties
of how the network functions. When every node is independent, the network is
maximally \textit{expressive}: if we define the network's ``state'' as the
total set of activity patterns across nodes, then every state is equally
reachable by a network with fully independent nodes. On the other hand, a fully
coupled network optimizes \textit{robustness}: any subset of nodes, other than
the entire network, may be removed from the network without any loss of
function or expressive power. Note that a given set of nodes might reconfigure
its connections or behaviors under different circumstances to change its
position along this continuum according to the needs at hand. Presumably, most
systems tend to occupy positions between the above extremes. We wondered: might
the human brain reconfigure itself to be more flexible or more robust according
to ongoing demands?
